VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added literature review

 \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}

@@

{\it MSC 2010\/}: Primary 26A33;
                  Secondary 33E12, 34A08, 34K37, 35R11, 60G22, ...

@@

{\it Key Words and Phrases}: fractional calculus, Mittag-Leffler
type functions, fractional ordinary and partial differential
equations, ...

@@

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884} by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
%As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
%the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
%We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. 
%The geometric interpretation that we present in this paper here is an extension of the geometric interpretation presented by Podlubny  
Podlubny showed that a Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral. The Riemann-Stieltjes integral so obtained can then be visualized using Bullock's geometric framework. Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}. Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{gamma.pdf}
\caption{A plot of $\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt$ for $x\in(-5,5)$. $\Gamma(x)$ is not defined for the negative integers. Moreover, it is a natural extension of the factorial function to the real numbers \cite{euler1738}.}
\label{fig:gamma}
\end{figure}

@@

@@

\bibitem{GasRah}
 G. Gasper, M. Rahman,
 \emph{Basic Hypergeometric Series}.
 Cambridge University Press, Cambridge (1990).

@@

\bibitem{Kir}
 V. Kiryakova,
 A brief story about the operators of generalized
fractional calculus.
 \emph{Fract. Calc. Appl. Anal.} \textbf{11}, No 2 (2008), 201--218; DOI: ..........

@@

\bibitem{Moak}
 D.S. Moak,
 The $q$-analogue of the Laguerre polynomials.
\emph{J. Math. Anal. Appl.} \textbf{81}, No 1 (1981), 20--47. % ; doi: ........

@@

\bibitem{Rosbl}
 M. Rosenblum,
 Generalized Hermite polynomials and the Bose-like oscillator
 calculus.
 In: \emph{Operator Theory: Advances and Applications},
 Birkh\"auser, Basel (1994), 369--396.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 \noindent
   %(First) Author's full postal address
$^1$ Institute of Mathematics and Informatics \\
Bulgarian Academy of Sciences \\
"Acad. G. Bontchev" Str., Block 8 \\
Sofia -- 1113, BULGARIA  \\[4pt]
  e-mail: virginia@diogenes.bg
\hfill Received: November 1, 2014 \\[12pt]
  % Second Author's address
$^2$ Dept. of Physics, University of Bologna\\
Via Irnerio 46, I -- 40126 Bologna, ITALY \\[4pt]
  e-mail: .....

>>>>

 \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize T.L Grobler]{\normalsize Trienko Lups Grobler $^1$}

@@

{\it MSC 2010\/}: 26A33
                  %Secondary 33E12, 34A08, 34K37, 35R11, 60G22, ...

@@

{\it Key Words and Phrases}: geometric interpretation, fractional calculus, left-sided Riemann-Liouville integral, cavalieri integral.

@@

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884}. We accomplish this by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
%As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
%the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
%We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. 
%The geometric interpretation that we present in this paper here is an extension of the geometric interpretation presented by Podlubny  
Podlubny showed that a Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral. The Riemann-Stieltjes integral so obtained can then be visualized using Bullock's geometric framework. Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}. Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\

@@

% \begin{figure}[htb]
% \centering
% \includegraphics[width=0.7\textwidth]{gamma.pdf}
% \caption{A plot of $\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt$ for $x\in(-5,5)$. $\Gamma(x)$ is not defined for the negative integers. Moreover, it is a natural extension of the factorial function to the real numbers \cite{euler1738}.}
% \label{fig:gamma}
% \end{figure}

@@

\bibitem{ackermann12} E.R.~Ackermann, T.L~Grobler, W.~Kleynhans,~W., J.C.~ Olivier, B.P.~Salmon, A.J.~van Zyl. Cavalieri
Integration. \textit{Quaest. Math.} \textbf{35}, No 3 (2012), 265--296.

\bibitem{adda97} F.B.~Adda, (1997). Geometric interpretation of the fractional derivative. \textit{J. of Fract. Calc.} \textbf{11}, (1997), 21--52.

\bibitem{bullock88} G.L.~Bullock. A geometric interpretation of the Riemann-Stieltjes integral. \textit{Am. Math. Mon.} \textbf{95}, No 5 (1988), 448--455.

%\bibitem{bartle76} R.G.~Bartle, \textit{The Elements of Real Analysis.} Wiley, New York (1976).

%Physical
%\bibitem{cioc16} Cioc, R. (2016). Physical and geometrical interpretation of Gr\"{u}nwald-Letnikov differintegrals: Measurement of path and acceleration. \textit{Fract. Calc. Appl. Anal.} 19(1): 161--172.

%\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869

%\bibitem{euler1738} Euler,~L. (1738). De progressionibus transcendentibus seu quarum termini generales algebraice dari nequeunt. \textit{Commentarii academiae scientiarum Petropolitanae}. 36--57.

\bibitem{garcia2019} J.P.~Garc\'{i}a-Sandoval, On representation and interpretation of Fractional calculus and fractional order systems. \textit{Fract. Calc. Appl. Anal.}, \textbf{22}, No 2 (2019), 522---537.

%\bibitem{gomez14} J.F~Gomez-Aguilara, R.~Razo-Hernandez, D.A.~Granados-Lieberman. Physical interpretation of fractional
%calculus in observable terms: analysis of the fractional time constant and the transitory response. \textit{Revista Mexicana de Fisica.} \textbf{60}, (2014), 32--38.

\bibitem{grobler19} T.L.~Grobler. Visualization of the Riemann-Stieltjes integral. \textit{Coll. Math. J.} \textbf{50}. No 3 (2019), 198--209.

\bibitem{laurent1884} H.~Laurent, (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} \textbf{3}, No 3 (1884), 240--252.

%\bibitem{liouville1832} Liouville,~J. (1832). M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices 
%que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.

\bibitem{machado03} J.T.~Machado. A probabilistic interpretation of the fractionalorder differentiation. \textit{Fract. Calc. Appl. Anal.} \textbf{6}, No 1 (2003), 73--80.

%\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.

\bibitem{machado17} J.T.~Machado, V.~Kiryakova. The chronicles of fractional calculus. \textit{Fract. Calc. Appl. Anal.} \textbf{20}, No 2 (2017), 307--336.

%\bibitem{munkhammar05} Munkhammar,~J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergrad. Math. J.}, 6(1): 6.

%physical
\bibitem{nigmatullin92} R.R.~Nigmatullin. A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} \textbf{90}, No 3 (1992): 242--251.

\bibitem{podlubny02} Podlubny,~I. Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} \textbf{5}, No 4 (2002), 367--386.

%\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.

%\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.

\bibitem{ross06} B.Ross, (Ed.). \textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, \textbf{457}, Springer (1974).

\bibitem{rutman95} R.S.~Rutman. On physical interpretations of fractional integration and differentiation. \textit{Theor. and Math. Phys.} \textbf{105}, No 3 (1994),1509--1519.

 %Probability
\bibitem{stanislavsky04} A.A.~Stanislavsky.  Probability interpretation of the integral of fractional order, \textit{Theor. and Math. Phys.} \textbf{138}, No 3 (2004), 418--431.

%Geometric
\bibitem{tarasov16} V.E.~Tarasov. Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} \textbf{19}, No 5 (2016), 1200--1221.

%Economic
\bibitem{tarasova17} V.V.~Tarasova, V.E.~Tarasov. Economic Interpretation of Fractional Derivatives. \textit{Prog. in Fract. Diff. and Appl.} \textbf{3}, No 1 (2017), 1--7.

@@

%\bibitem{GasRah}
% G. Gasper, M. Rahman,
% \emph{Basic Hypergeometric Series}.
% Cambridge University Press, Cambridge (1990).

@@

%\bibitem{Kir}
% V. Kiryakova,
% A brief story about the operators of generalized
%fractional calculus.
% \emph{Fract. Calc. Appl. Anal.} \textbf{11}, No 2 (2008), 201--218; DOI: ..........

@@

%\bibitem{Moak}
% D.S. Moak,
% The $q$-analogue of the Laguerre polynomials.
%\emph{J. Math. Anal. Appl.} \textbf{81}, No 1 (1981), 20--47. % ; doi: ........

@@

%\bibitem{Rosbl}
% M. Rosenblum,
% Generalized Hermite polynomials and the Bose-like oscillator
% calculus.
% In: \emph{Operator Theory: Advances and Applications},
% Birkh\"auser, Basel (1994), 369--396.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 \noindent
   %(First) Author's full postal address
$^1$ Dept. of Mathematical Sciences, Stellenbosch University \\
Private Bag X1 --- 7600 SOUTH AFRICA \\[4pt]
  e-mail: tlgrobler@sun.ac.za
\hfill Received: November 1, 2014 \\[12pt]
  % Second Author's address
%$^2$ Dept. of Physics, University of Bologna\\
%Via Irnerio 46, I -- 40126 Bologna, ITALY \\[4pt]
%  e-mail: .....
